\bf Properties and Bayesian fitting of restricted Boltzmann machines

### 2018-09-05 writing/paper-rbm/docs/paper.tex
fix citation

\leavevmode\hypertarget{ref-sculley2018winner}{}%
Sculley, D, Jasper Snoek, Alex Wiltschko, and Ali Rahimi. 2018.
``Winner's Curse? On Pace, Progress, and Empirical Rigor.''

>>>>

\leavevmode\hypertarget{ref-sculley2018winner}{}%
Sculley, D., Jasper Snoek, Alex Wiltschko, and Ali Rahimi. 2018.
``Winner's Curse? On Pace, Progress, and Empirical Rigor.'' In \emph{6th
International Conference on Learning Representations Workshop
Submission}. \url{https://openreview.net/forum?id=rJWF0Fywf}.
